$\our$: Simple Contrastive Pretraining for \\ Large Document Embeddings

### 2023-06-23 emnlp2023-latex/paper.tex
changes
update the figures

\title{DocSplit: Simple Contrastive Pretraining for \\ Large Document Embeddings}

@@

Our total compute is relatively small and so we have a small environmental impact.
Pretraining \ourbert took 4 days on an Nvidia 2080 GPU with 11GB of RAM,
and pretraining \ourlong took 4 days with a \fixme{GPU}.
Other models use larger GPU clusters that require considerably more energy.
The finetuning procedures run in less than 1 day on the same systems.

@@

>>>>

\title{$\our$: Simple Contrastive Pretraining for \\ Large Document Embeddings}

@@

Our total compute is relatively small and so we have a small environmental impact.
Pretraining \ourbert took 4 days on an Nvidia 2080 GPU with 11GB of RAM,
and pretraining \ourlong took 4 days with an Nvidia Quadro RTX 8000 with 48GB of RAM.
Other models use larger GPU clusters that require considerably more energy.
The finetuning procedures run in less than 1 day on the same systems.

@@

\subsection{Few-shot Learning}
\begin{table}
    \centering
    \input{fig/results-few_shot.tex}
    \caption{Few-shot classification on five datasets. }
    \vspace{-3mm}
    \label{tab:few_shot}
\end{table}
Table~\ref{tab:few_shot} shows the results of few-shot text classification on these five datasets. 
We can see that, under the same model structure, \our~(i.e.,~\our$_{\mathrm{bert}}$ and \our$_{\mathrm{long}}$) achieves $12.0\%$ and $24.3\%$ macro-F1 improvements compared to SimCSE and Longformer respectively. 
Surprisingly, INSTRUCTOR achieves low performance on the NYT and BBCNews under few-shot settings.
These improvements are higher than standard text classification.
